Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use apply achine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means. This paper reports on a research applying machine-driven approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
Research combining machine learning  and  image  informatics tools and techniques allow us to rapidly enrich the metadata currently associated with the digitized specimens. The study focuses on a sample of 7244 images from the Illinois Natural History Survey (INHS), which also included additional, manually generated image-quality metadata Results show we can  accurately generate metadata for six key %6? 
metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
%to confirm list
%jg to add note about x, y, z, unless someone else does first
The automatic process out-performs humans in terms and cost, and provides a solution for leveraging digitized specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

>>>>

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use apply achine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means. This paper reports on a research applying machine-driven approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
Research combining machine learning  and  image  informatics techniques allow us to rapidly enrich existing metadata associated for a sample of 7244 images from the Illinois Natural History Survey (INHS). The sample also includes 22 manually generated image-quality metadata properties, aiding our comparsion.  Results show we can  accurately generate metadata for six key %6? 
metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
%to confirm list of six properties.
%x, y, z = any other key results. jg will add from results sectin, unless someone else does first. 
The automatic process out-performs humans in terms and cost, and provides a novel solution for leveraging digitized specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
